\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-06-21 AffineLieAlgebras/InformalNotes/article.tex
Bibliography fixed

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then
the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and
it is clear that $\Delta^{+}_{\bot}$ is empty.
On the other hand
non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
through the chain of maximal embeddings
$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
The maximal regular embeddings are constructed by the exclusion of one or two roots
from the extended Dynkin diagram of the algebra. Since this process can give us
non-connected Dynkin diagrams we can see which roots are orthogonal to the root
space of non-maximal regular subalgebra $\mathfrak{a}$.  The complete classification of the regular subalgebras of affine Lie algebras can be found in the recent paper \cite{JPhysA2008}.

@@

The set $\Delta^{+}_{\bot}$ contains the roots
\begin{equation}
  \label{eq:27}
  \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
\end{equation}
and is the set of positive roots for the algebra $\mathfrak{a}_{\bot}=B_2$.

@@

The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.
\begin{figure}[p]
  \centering
    \includegraphics[width=90mm,height=90mm]{B4_B2_anom_points.pdf}
  \caption{Projected weights of $\pi_{B_2}\left(\Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[height=80mm]{B4_B2_fan.pdf}
  \caption{The fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
Applying the recurrent relation (\ref{recurrent-relation}) we obtain the
following branching coefficients:
\begin{multline}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+\\
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}.
\end{multline}

@@

The task of the construction of non-diagonal modular invariants is not easy, although the complete classification of modular invariants for some models is known [116, 219, 117, 119, 46] in \cite{Fuchs:2009iz}.

@@

The folded fan technique \cite{IKL2010}  can be used to get the explicit expression for the branching functions and the corresponding coset conformal field theory characters. This subject will be discussed in the future works.

>>>>

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then
the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and
it is clear that $\Delta^{+}_{\bot}$ is empty.
On the other hand
non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
through the chain of maximal embeddings
$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
The maximal regular embeddings are constructed by the exclusion of one or two roots
from the extended Dynkin diagram of the algebra. Since this process can give us
non-connected Dynkin diagrams we can see which roots are orthogonal to the root
space of non-maximal regular subalgebra $\mathfrak{a}$.  The complete classification of the regular subalgebras of affine Lie algebras can be found in the recent paper \cite{1751-8121-41-36-365204}.

@@

The set $\Delta^{+}_{\bot}$ contains the roots
\begin{equation}
  \label{eq:27}
  \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
\end{equation}
and is the set of positive roots for the algebra $\mathfrak{a}_{\bot}=B_2$.
\begin{figure}[p]
  \centering
    \includegraphics[width=90mm,height=90mm]{B4_B2_anom_points.pdf}
  \caption{Projected weights of $\pi_{B_2}\left(\Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[height=80mm]{B4_B2_fan.pdf}
  \caption{The fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}

@@

The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.

Applying the recurrent relation (\ref{recurrent-relation}) we obtain the
following branching coefficients:
\begin{multline}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+\\
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}.
\end{multline}

@@

The task of the construction of non-diagonal modular invariants is not easy, although the complete classification of modular invariants for some models is known \cite{1994hepthGannon,1995JMPGannon}.

@@

The folded fan technique \cite{il2010folded} can be used to get the explicit expression for the branching functions and the corresponding coset conformal field theory characters. This subject will be discussed in the future works.
